---
title: "Anthracological Assessment of Post-Settlement Soils in Fundy Provincial Park "
date: "`r format(Sys.Date())`"
author:
- Nabiha Tasnuv^1^*
- Sydney Teresa Battist^1^*
- Thuy Thi Ngoc Le^1^*

output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
editor_options: 
  markdown: 
    wrap: 72
---
```{css, echo=FALSE}
p.caption {
  font-size: 18px;
}
```

# **AFFILIATIONS** {-}
^1^Mount Allison University, New Brunswick, Canada  
* corresponding author


# **ACKNOWLEDGEMENTS** {-}
Ben Phiplip



# **INTRODUCTION**

## Background  



## Research Question   



## Hypothesis   




## Prediction   





# **MATERIALS & METHODS** 
## Set Chunk Options
Formatted display of content from .md file on GitHub site.
Upon knitr figures will be saved to 'Figs/'.
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, error = FALSE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

## Load Packages
```{r packages, include = FALSE}
library(tidyverse) #core packages from Tidyverse
library(googledrive) #access to Google Drive
library(googlesheets4) #access to Google Sheets
library(lubridate) #tidyverse handling dates & times
library(knitr) #make table
```

## Connect to Google Account
```{r connect_google}
#Instead of sending a token, Google Sheets4 will send an API key. This can be used to access public resources for which no Google sign-in is required.

# Deauthorize to access public sheets
gs4_deauth()

#URL of the Google Sheet so that it is available to anyone
googlesheet_url <- "https://docs.google.com/spreadsheets/d/1u14lKzqxOS3QofUmpfmVJ3RpYHt1jMNrFTxg_J5v4Qc/edit?usp=sharing"
```


## Accessing Data From Google Sheets
```{r accessing_sheets}
 Diversity <- read_sheet(googlesheet_url, sheet = "diversity")
 Charcoal <- read_sheet(googlesheet_url, sheet = "charcoal")
```



